Wigglyhedra

### 2025-01-09 MZ/answerReferee.tex

\item \textsl{\color{gray} pg.\,31 (C2): ``up to equivalence'' should probably also include ``up to scalar multiplication''; same for ``unique element''.} \\
Thanks! Fixed.

\item \textsl{\color{gray} pg.\,32 (C1)*: As mentioned in the previous section, some sort of ``up to appropriate shift in gradings'' should be included.} \\
Thanks! Fixed.

\end{itemize}

Finally, we have also added Figure 15 providing a stereographic projection of the wiggly fan with vertices labeled by the corresponding wiggly arcs, and we have labeled the vertices of the wigglyhedron in Figure 16 by the corresponding wiggly pseudotriangulations.
We have also corrected a few additional typos.

### 2025-01-09 draft/wigglyhedra.tex
improve two pictures

We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$ illustrated in \cref{fig:wigglyFan}.
\afterpage{
\begin{figure}
\centerline{\includegraphics[scale=.75]{wigglyFan}}
\caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane.}
\label{fig:wigglyFan}
\end{figure}
}

@@

We now construct the wigglyhedron illustrated in \cref{fig:wigglyhedron} when~${n = 2}$.
%
\afterpage{
\begin{figure}
\centerline{\input{wigglyhedron}}
\caption{The wigglyhedron~$\wigglyhedron_2$.}
\label{fig:wigglyhedron}
\end{figure}
}

>>>>

We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$ illustrated in \cref{fig:wigglyFan}.
\afterpage{
\begin{figure}
\centerline{\includegraphics[scale=.75]{wigglyFanLabeled}}
\caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane. The vertices of the projection are rays of~$\wigglyFan_2$ and are labeled by the corresponding wiggly arcs. Compare with \cref{fig:wigglyComplex}\,(left).}
\label{fig:wigglyFan}
\end{figure}
}

@@

We now construct the wigglyhedron illustrated in \cref{fig:wigglyhedron} when~${n = 2}$.
%
\afterpage{
\begin{figure}
%\centerline{\input{wigglyhedron}}
\centerline{\includegraphics[scale=.75]{wigglyhedron}}
\caption{The wigglyhedron~$\wigglyhedron_2$. The vertices are labeled by the corresponding wiggly pseudotriangulations. Compare to \cref{fig:wigglyComplex}\,(right) and \cref{fig:wigglyLattice}\,(left).}
\label{fig:wigglyhedron}
\end{figure}
}
